Wavelets

### 2019-02-23 Write_up/Writing/Introduction_outline.Rmd
some bits

## Satellite SST data

This study made use of four satellite-derived Sea surface temperatures (SST) datasets and the SACTN in situ coastal SST have been observed by satellite instruments since 1981 and are regarded as one of the longest satellite-based records of any earth climate variable (REFERENCE). The National Oceanic and Atmospheric Administration (NOAA) ¼° daily Optimum Interpolation Sea Surface Temperature (OISST) is an analysis of different platforms (satellites, ships and buoys) on a global grid. This gridded daily SST product assimilates both remotely sensed and in situ sources of data to create a level-4 gap free product (Banzon et al., 2016). A spatially complete sea suface temperature map is produced by interpolation to fill in gaps within the dataset. The method used to fill these gaps includes the adjustment of satellite and ship observations which compensate for the bias differences (REFERENCE). There are two types of daily OISST, named after the relevant satellite sensors. These are the Advanced Very High Resolution Radiometer (AVHRR) and Advanced Microwave Scanning Radiometer on the Earth Observing System (AMSR-E). Currently the AVHRR has the longest record starting from 1981 to the present. Infrared instruments, like AVHRR, can make observations at relatively high resolutions. Microwave instruments, like AMSR-E, can measure SSTs in most weather conditions but not adjacent to land. The AVHRR-only Optimally-Interpolated Sea Surface. Temperature (OISST) was used to determine SST within the study region. The AVHRR datasets have been provided global SSTs for more than four decades (Reynolds and Smith, 1994; Pearce et al 2006).

@@

>>>>

## Satellite data

This study made use of four satellite-derived Sea Surface Temperatures (SST) datasets and the SACTN in situ coastal SST have been observed by satellite instruments since 1981 and are regarded as one of the longest satellite-based records of any earth climate variable (REFERENCE). The National Oceanic and Atmospheric Administration (NOAA) ¼° daily Optimum Interpolation Sea Surface Temperature (OISST) is an analysis of different platforms (satellites, ships and buoys) on a global grid. This gridded daily SST product assimilates both remotely sensed and in situ sources of data to create a level-4 gap free product (Banzon et al., 2016). A spatially complete sea suface temperature map is produced by interpolation to fill in gaps within the dataset. The method used to fill these gaps includes the adjustment of satellite and ship observations which compensate for the bias differences (REFERENCE). There are two types of daily OISST, named after the relevant satellite sensors. These are the Advanced Very High Resolution Radiometer (AVHRR) and Advanced Microwave Scanning Radiometer on the Earth Observing System (AMSR-E). Currently the AVHRR has the longest record starting from 1981 to the present. Infrared instruments, like AVHRR, can make observations at relatively high resolutions. Microwave instruments, like AMSR-E, can measure SSTs in most weather conditions but not adjacent to land. The AVHRR-only Optimally-Interpolated Sea Surface. Temperature (OISST) was used to determine SST within the study region. The AVHRR datasets have been provided global SSTs for more than four decades (Reynolds and Smith, 1994; Pearce et al 2006).

@@

```{r}
wc <- site_list %>% 
  filter(coast == "wc")
save(wc, file = "wc.csv")
```

### 2019-02-23 studysite_plot.Rmd
fixed
some bits

# Plotting with pixel boxes
fig1 <- ggplot() +#coord_equal() + 
  geom_raster(data = sa_bathy, aes(x = lon, y = lat, fill = depth)) +
  #geom_raster(data = isobath200, aes(x = lon, y = lat, fill = coast)) +
  stat_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth, alpha = ..level..), 
               colour = "black", size = 0.2, binwidth = 200, na.rm = TRUE, show_guide = FALSE) +
  geom_polygon(data = south_africa_coast, aes(x = lon, y = lat, group = group), 
               size = 1, colour = "black", fill = "white") +
  geom_path(data = sa_provinces_new, aes(x = long, y = lat, group = group)) +
  geom_polygon(data = wcBox, aes(x = lon, y = lat, group = group), alpha = 0.20, 
               colour = "bisque1", fill = "bisque1") +
  geom_point(data = metaData2, aes(x = lon, y = lat), alpha = 0.8, size = 1.6) +
  geom_point(data = site_pixels, aes(x = lon, y = lat), colour = "white", shape = 0, alpha = 0.8, size = 2.1) +
  geom_rect(data = test, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), 
            alpha = 0.4, colour = "red", size = 0.1, linetype = 1) +
  scale_alpha_continuous(breaks = c(-200, -1000, -2000, -3000, -4000, -5000),
                         guide_legend(title = "depth (m)")) +
  scale_fill_gradient(low = "dodgerblue4", high = "dodgerblue", na.value = "steelblue4", 
                      breaks = c(-1000, -2000, -3000, -4000, -5000),
                      guide_legend(title = "depth (m)")) +
  labs(title = NULL, x = NULL, y = NULL) +
  guides(colour = guide_legend(override.aes = list(size = 3))) +
  #guide_legend(ncol = 2) +
  theme(legend.key = element_rect(colour = NA, size = 0.2),
        legend.key.height = unit(0.4, "cm"),
        legend.background = element_blank()) +
        #legend.justification = c(1,0), legend.position = c(0.5, 0.4)) +
  coord_cartesian(xlim = sa_lons, ylim = sa_lats)
```

>>>>

# Plotting with pixel boxes
fig1 <- ggplot() +#coord_equal() + 
  geom_raster(data = sa_bathy, aes(x = lon, y = lat, fill = depth)) +
  #geom_raster(data = isobath200, aes(x = lon, y = lat, fill = coast)) +
  stat_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth, alpha = ..level..), 
               colour = "black", size = 0.2, binwidth = 200, na.rm = TRUE, show_guide = FALSE) +
  geom_polygon(data = south_africa_coast, aes(x = lon, y = lat, group = group), 
               size = 0.5, colour = "black", fill = "white") +
  #geom_path(data = sa_provinces_new, aes(x = long, y = lat, group = group)) +
  geom_polygon(data = wcBox, aes(x = lon, y = lat, group = group), alpha = 0.20, 
               colour = "bisque1", fill = "bisque1") +
  geom_point(data = metaData2, aes(x = lon, y = lat), alpha = 0.8, size = 1.6) +
  geom_point(data = site_pixels, aes(x = lon, y = lat), colour = "white", shape = 0, alpha = 0.8, size = 2.1) +
  geom_rect(data = test, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), 
            alpha = 0.4, colour = "red", size = 0.1, linetype = 1) +
  scale_alpha_continuous(breaks = c(-200, -1000, -2000, -3000, -4000, -5000),
                         guide_legend(title = "depth (m)")) +
  scale_fill_gradient(low = "dodgerblue4", high = "dodgerblue", na.value = "steelblue4", 
                      breaks = c(-1000, -2000, -3000, -4000, -5000),
                      guide_legend(title = "depth (m)")) +
  labs(title = NULL, x = NULL, y = NULL) +
  guides(colour = guide_legend(override.aes = list(size = 3))) +
  #guide_legend(ncol = 2) +
  theme(legend.key = element_rect(colour = NA, size = 0.2),
        legend.key.height = unit(0.4, "cm"),
        legend.background = element_blank()) +
        #legend.justification = c(1,0), legend.position = c(0.5, 0.4)) +
  coord_cartesian(xlim = sa_lons, ylim = sa_lats)
#ggsave("Figures/fig1.pdf", width = 7.5, height = 3.5, pointsize = 10)
```

### 2019-02-23 wavelets.Rmd
some bits

SACTN_fyears <- filtered_years(df = overlap_ts) 
MUR_fyears <- filtered_years(df = insitu_MUR) 
OISST_fyears <- filtered_years(df = insitu_OISST) 
G1SST_fyears <- filtered_years(df = insitu_G1SST) 
K10_fyears <- filtered_years(df = insitu_K10) 
```

@@

# temp.d <- temp.d(df = MUR_fyears) 
# temp.d <- temp.d(df = OISST_fyears)
# temp.d <- temp.d(df = G1SST_fyears) 
temp.d <- temp.d(df = K10_fyears)

>>>>

SACTN_fyears <- filtered_years(df = overlap_ts) 
MUR_fyears <- filtered_years(df = insitu_MUR) 
OISST_fyears <- filtered_years(df = insitu_OISST) 
G1SST_fyears <- filtered_years(df = insitu_G1SST) 
K10_fyears <- filtered_years(df = insitu_K10)

save(SACTN_fyears, file = "Data/temp_2014_2015/SACTN_fyears.RData")
save(MUR_fyears, file = "Data/temp_2014_2015/MUR_fyears.RData")
save(OISST_fyears, file = "Data/temp_2014_2015/OISST_fyears.RData")
save(G1SST_fyears, file = "Data/temp_2014_2015/G1SST_fyears.RData")
save(K10_fyears, file = "Data/temp_2014_2015/K10_fyears.RData")
```

@@

# temp.d <- temp.d(df = SACTN_fyears) 
# temp.d <- temp.d(df = MUR_fyears) 
# temp.d <- temp.d(df = OISST_fyears)
# temp.d <- temp.d(df = G1SST_fyears) 
temp.d <- temp.d(df = K10_fyears)
